Automated Verification and Synthesis of Embedded Systems: Advances and Challenges

### 2017-01-02 paper.tex
review "Verification and Synthesis Challenges for Embedded Systems"

In this respect, DSVerifier has been extended to automatically synthesize digital stabilizing controllers for continuous plants~\cite{Abate17}. In particular, a counter-example guided inductive synthesis approach, implemented in a tool called digital system synthesizer (DSSynth), uses inductive synthesis in conjunction with DSVerifier's algorithm for verifying robust closed-loop stability that addresses plant variations as interval sets as well as FWL uncertainties in digital controllers. DSSynth is able to successfully synthesize stable digital controllers for a set of intricate plant models taken from the literature within minutes.

@@

%--------------------------------------
\section{Verification Challenges}
\label{Verification-Challenges} 
%--------------------------------------

@@

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.

%In summary, the main challenge when verifying embedded systems lies on improving coverage, where more system's functions are verified, and reducing verification time, {\it i.e.}, pruning the state-space exploration during verification. These aspects are of extreme relevance in micro-grids to ensure reliability, which is a key issue for (smart) cities and consumers.

>>>>

In this respect, DSVerifier has been extended to automatically synthesize digital stabilizing controllers for continuous plants~\cite{Abate17}. In particular, a CEGIS-based approach, implemented in a tool called digital system synthesizer (DSSynth), uses inductive synthesis in conjunction with DSVerifier's algorithm for verifying robust closed-loop stability that addresses plant variations as interval sets as well as FWL uncertainties in digital controllers. DSSynth is able to successfully synthesize stable digital controllers for a set of intricate plant models taken from the control literature within minutes.

@@

%--------------------------------------
\section{Verification and Synthesis \\ Challenges for Embedded Systems}
\label{Verification-Challenges} 
%--------------------------------------

@@

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. In particular, software developed for that type of embedded systems has been extensively tested and verified, and also optimized for efficiency over years of development. Therefore, when a new product is derived from a given platform, a lot of legacy code is usually reused for improving development time and code quality. Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.

Those five challenges place additional difficulties for developing reliable synthesizers for embedded systems, especially for cyber-physical systems and micro-grids, where the controlled object ({\it e.g.}, physical plant) typically exhibits continuous behavior whereas the controller (usually implemented by a real-time computer system) operates in discrete time and over a quantized domain. In particular, synthesizers for those systems need to consider the effects of the quantizers (A/D and D/A converters) when a digital equivalent of the controlled object is considered, {\it i.e.}, a model of their physical environment (cf. intelligent product in Figure~\ref{intelligent-product}). Additionally,  finite-precision arithmetic and their related rounding errors need to be considered when correct-by-construction code is generated for embedded systems.
